PANCHANGE_analysis

### 2020-08-18 PANCHANGE_analysis.Rmd
changes

```{r dat.coping summary}
summarytools::dfSummary(
  dat,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

>>>>

```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

Data availability
```{r gad availability}
dat %>%
  freq(
    data_group_gad,
    cumul = F)
```

```{r phq availability}
dat %>%
  freq(
    data_group_phq,
    cumul = F)
```

```{r pcl availability}
dat %>%
  freq(
    data_group_pcl,
    cumul = F)
```
